Interactive Graphics for Visually Diagnosing Forest Classifiers in R

### 2022-06-29 PPforestVizupdate.Rnw
Fig 3 code change

@
 \vspace*{-0.3cm}
 \caption{Decision boundaries for PPtree algorithm on 2D simulated data. The partitions generated by PPtree algorithm are oblique to the axis, incorporating the association between the two variables.\label{bounds}}
\end{figure}
Two data set are used in this paper, crab ~\citep{CM74} and fishcatch data~\citep{fishcatch}. To illustrate the mapping of diagnostics to visualization crab data are used because of its simplicity. The second data set is introduced to illustrate the interactive web app which combines the visualizations introduced in this paper and present a more complex problem to explore within the application.

@@

d_boundary <- function(node){
  indtree <- ppf[["output.trees"]][[tree]]
  sel <- (1:(ncol(ppf$train) - 1))[indtree$projbest.node[node, ] !=0]
  if(node%in%1) dat = dat_2d(node)
  if(node%in%2) dat = dat_2d(node) %>%  filter(Type %in% c("OrangeFemale", "OrangeMale") )
  if(node%in%3) dat = dat_2d(node) %>%  filter(Type %in% c("BlueFemale", "BlueMale") )

@@

  if(node%in%1){
    p1 <- p1 +  scale_colour_brewer(name = "Class", type = "qual", palette = "Dark2")
  }
  if(node%in%2){
    p1 <-   p1 +  scale_color_manual(values = myColors[3:4])
  }
  if(node%in%3){
    p1<-  p1 +  scale_color_manual(values = myColors[1:2])
  }
  p1
}

@@

 Interaction is added to the plots described in Section \ref{visen} as well as other plots, which are organized into an interactive web app using \verb#shiny#~\citep{chang11shiny, wickham2021mastering} for exploring the ensemble model. The app is organized into three tabs: individual cases; models; and performance comparison, to provide a model diagnostic tool. Interaction is provided as mouse-over labeling, mouse-click selection and brushing, with results linked across multiple plots. The app takes advantage of new tools provided in the \verb#plotly#~\citep{plotly} package, developed as a part of Sievert's PhD thesis research~\citep{sievertthesis}.

>>>>

@
 \vspace*{-0.3cm}
 \caption{Decision boundaries for PPtree algorithm on 2D simulated data. The partitions generated by PPtree algorithm are oblique to the axis, incorporating the association between the two variables.\label{bounds}}
\end{figure}
Two data set are used in this paper, crab~\citep{CM74} and fishcatch data~\citep{fishcatch}. To illustrate the mapping of diagnostics to visualization crab data are used because of its simplicity. The second data set is introduced to illustrate the interactive web app which combines the visualizations introduced in this paper and present a more complex problem to explore within the application.

@@

d_boundary <- function(node){
  indtree <- ppf[["output.trees"]][[tree]]
  sel <- (1:(ncol(ppf$train) - 1))[indtree$projbest.node[node, ] !=0]
  if(node%in%1) dat = dat_2d(node)
  if(node%in%2) dat = dat_2d(node) %>%  filter(Type %in% c("BlueMale", "OrangeMale") )
  if(node%in%3) dat = dat_2d(node) %>%  filter(Type %in% c("BlueFemale", "OrangeFemale") )

@@

  if(node%in%1){
    p1 <- p1 +  scale_colour_brewer(name = "Class", type = "qual", palette = "Dark2")
  }
  if(node%in%2){
    p1 <-   p1 +  scale_color_manual(values = myColors[c(2,4)])
  }
  if(node%in%3){
    p1<-  p1 +  scale_color_manual(values = myColors[c(1,3)])
  }
  p1
}

@@

 Interaction is added to the plots described in Section \ref{visen} as well as other plots, which are organized into an interactive web app using \verb#shiny#~\citep{chang11shiny, wickham2021mastering} for exploring the ensemble model. The app is organized into three tabs: individual cases; models; and performance comparison, to provide a model diagnostic tool. Interaction is provided as mouse-over labeling, mouse-click selection and brushing, with results linked across multiple plots. The app takes advantage of new tools provided in the \verb#plotly# package ~\citep{plotly,sievert2020interactive}, developed as a part of Sievert's PhD thesis research~\citep{sievertthesis}.
